Summary of PM2.5 Nonattainment  Analysis

### 2020-11-09 Analysis Files/Paper_Analysis_327.Rmd
add method variables

# Propensity Score Analysis - Updated to include Random Forest!
```{r, echo=FALSE}
###############################################################
#####     Estimate the Propensity Score      ##################
###############################################################
dat$CompletelyRural = as.numeric(dat$CompletelyRural)
# -- Full model using only summary health outcomes
fullmodel = glm(a~.  + avgrelhum*avgtemp + pmbase*avgtemp, family=binomial(link="logit"), data = dat[, names(dat) %in% c(covariates, "a") & !(names(dat) %in% c("Monitor", "TotPop", "COPDrate", "CVstrokerate", "HFrate", "HRDrate", "IHDrate", "PVDrate", "RTIrate")), with = FALSE]) #"mortrate", "resprate", "CVDrate"

@@

# dat$ps = get_propensity_scores()
dat$ps = get_propensity_scores(method="RF")

>>>>

# Propensity Score Analysis - Updated to include Random Forest!
```{r, echo=FALSE}
###############################################################
#####     Estimate the Propensity Score      ##################
###############################################################

method = "RF"

dat$CompletelyRural = as.numeric(dat$CompletelyRural)
# -- Full model using only summary health outcomes
fullmodel = glm(a~.  + avgrelhum*avgtemp + pmbase*avgtemp, family=binomial(link="logit"), data = dat[, names(dat) %in% c(covariates, "a") & !(names(dat) %in% c("Monitor", "TotPop", "COPDrate", "CVstrokerate", "HFrate", "HRDrate", "IHDrate", "PVDrate", "RTIrate")), with = FALSE]) #"mortrate", "resprate", "CVDrate"

@@

# dat$ps = get_propensity_scores()
dat$ps = get_propensity_scores(method=method)
